\documentclass[12pt,a4paper]{amsart}
% ukazi za delo s slovenscino -- izberi kodiranje, ki ti ustreza
\usepackage[slovene]{babel}
\usepackage[utf8]{inputenc}
%\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{url}
%\usepackage[normalem]{ulem}
\usepackage[dvipsnames,usenames]{color}
\usepackage{caption}
\usepackage{lipsum}
\usepackage{tikz}

\usetikzlibrary{graphs}
\usetikzlibrary{graphs.standard}

%\makeatletter
%\renewcommand\section{\@startsection{section}{1}%
%  \z@{.5\linespacing\@plus.7\linespacing}{.5\linespacing}%
%  {\normalfont\scshape\large\centering}}
%\renewcommand\subsection{\@startsection{subsection}{2}%
%  \z@{.5\linespacing\@plus.7\linespacing}{.5\linespacing}%
%  {\normalfont\scshape}}
%\renewcommand\subsubsection{\@startsection{subsubsection}{3}%
%  \z@{.5\linespacing\@plus.7\linespacing}{-.5em}%
%  {\normalfont\itshape}}
%\makeatother

% ne spreminjaj podatkov, ki vplivajo na obliko strani
\textwidth 15cm
\textheight 24cm
\oddsidemargin.5cm
\evensidemargin.5cm
\topmargin-5mm
\addtolength{\footskip}{10pt}
\pagestyle{plain}
\overfullrule=15pt % oznaci predlogo vrstico


% ukazi za matematicna okolja
\theoremstyle{definition} % tekst napisan pokoncno
\newtheorem{definicija}{Definition}[section]
\newtheorem{primer}[definicija]{Example}
\newtheorem{opomba}[definicija]{Remark}

\renewcommand\endprimer{\hfill$\diamondsuit$}

\theoremstyle{plain} % tekst napisan posevno
\newtheorem{lema}[definicija]{Lemma}
\newtheorem{izrek}[definicija]{Theorem}
\newtheorem{trditev}[definicija]{Statement}
\newtheorem{posledica}[definicija]{Corollary}
\newtheorem{conjecture}[definicija]{Conjecture}


% za stevilske mnozice uporabi naslednje simbole
\newcommand{\R}{\mathbb R}
\newcommand{\N}{\mathbb N}
\newcommand{\Z}{\mathbb Z}
\newcommand{\C}{\mathbb C}
\newcommand{\Q}{\mathbb Q}

% ukaz za slovarsko geslo
\newlength{\odstavek}
\setlength{\odstavek}{\parindent}
\newcommand{\geslo}[2]{\noindent\textbf{#1}\hspace*{3mm}\hangindent=\parindent\hangafter=1 #2}

% naslednje ukaze ustrezno popravi
\newcommand{\program}{Financial mathematics} % ime studijskega programa: Matematika/Finančna matematika
\newcommand{\imeavtorja}{Anej Rozman, Tanja Luštrek} % ime avtorja
\newcommand{\imementorja}{Assistant Professor Janoš Vidali} % akademski naziv in ime mentorja
\newcommand{\imesomentorja}{Professor Riste Škrekovski}
\newcommand{\naslovdela}{Rich-Neighbor Edge Colorings}
\newcommand{\letnica}{2023} %letnica diplome

\begin{document}

\thispagestyle{empty}
\noindent{\large
UNIVERSITY OF LJUBLJANA\\[1mm]
FACULTY OF MATHEMATICS AND PHYSICS\\[5mm]
\program\ -- 1st cycle}
\vfill

\begin{center}{\large
\imeavtorja\\[2mm]
{\bf \naslovdela}\\[10mm]
Term Paper in Finance Lab\\[2mm]
Short Presentation\\[1cm]
Advisers: \imementorja, \\ \imesomentorja\\[2mm]}
\end{center}
\vfill

\noindent{\large
Ljubljana, \letnica}
\pagebreak

\section{Introduction}

In this paper we set out to analyse an open conjecture in a modern graph theory problem known as rich-neighbor edge coloring.


\begin{definicija}
    In an edge coloring, an edge $e$ is called $rich$ if all edges adjacent to $e$ have different colors. An edge coloring is 
    called a $rich\text{-}neighbor \ edge \ coloring$ if every edge is adjacent to some rich edge.
\end{definicija}

\begin{definicija}
    $X'_{rn}(G)$ denotes the smallest number of colors for which there exists a rich-neighbor edge coloring.
\end{definicija}

\begin{conjecture}
    For every graph $G$ of maximum degree $\Delta$, $X'_{rn}(G) \leq 2\Delta - 1$ holds.
\end{conjecture}

\begin{primer}
    Let's take a look at the Petersen graph and an example of a rich-neighbor edge coloring.
    \begin{center}
        \begin{tikzpicture}[every node/.style={draw,circle, style={text opacity=0}}]
            \graph[clockwise, radius=3cm] {subgraph C_n [n=5,name=A] };
            \graph[clockwise, radius=1.5cm] {subgraph I_n [n=5,name=B] };
    
    
            % Define edge colors for the graph
            \draw[yellow, line width=1.3pt] (A 1) -- (B 1);
            \draw[blue, line width=1.3pt] (A 2) -- (B 2);
            \draw[green, line width=1.3pt] (A 3) -- (B 3);
            \draw[red, line width=1.3pt] (A 4) -- (B 4);
            \draw[cyan, line width=1.3pt] (A 5) -- (B 5);
            \draw[red, line width=1.3pt] (A 1) -- (A 2);
            \draw[cyan, line width=1.3pt] (A 2) -- (A 3);
            \draw[yellow, line width=1.3pt] (A 3) -- (A 4);
            \draw[blue, line width=1.3pt] (A 4) -- (A 5);
            \draw[green, line width=1.3pt] (A 5) -- (A 1);
            \draw[yellow, line width=1.3pt] (B 5) -- (B 2);
            \draw[cyan, line width=1.3pt] (B 4) -- (B 1);
            \draw[blue, line width=1.3pt] (B 3) -- (B 1);
            \draw[red, line width=1.3pt] (B 5) -- (B 3);
            \draw[green, line width=1.3pt] (B 4) -- (B 2);
        \end{tikzpicture}
    \end{center}
    We can see that for the Petersen graph (which is 3-regular) $X'_{rn}\leq 5$.
\end{primer}

\section{Plan}
    Our assingnment is to create an algorthm of sorts that ``proves'' the conjecture for regular graphs of degree 4 $\geq$ 
    (it finds a rich-neighbor edge coloring for every $k$-regular graph on $n$ verticies), 
    and to make a random search algorythm for checking classes of graphs that are too large to be checked individually.

\subsection{Integer Programming}
    Using SageMath we plan to create an integer programming model, that checks all smaller graphs for a rich-neighbor coloring with $\leq2\Delta - 1$ colors. Our interger program looks like this:
    $$
    \min t \\
    $$
    $$
    \forall e: \sum_{i=1}^{k} x_{ei} = 1 \\
    $$
    $$\forall i \ \forall u \ \forall v, w \sim u, v \neq u: x_{uv, i} + x_{uw, i} \leq 1 \\$$
    $$\forall e \ \forall i: x_{ei} \cdot i \leq 1 \\$$
    $$\forall uv \ \forall w \sim u, w \neq v \ \forall z \sim v, z \neq u, w \ \forall i: x_{uW, i} + x_{vz, i} + y_{uv} \leq 2 \\$$
    $$\forall e: \sum_{f \sim e}y_f \geq 1 \\$$
    $$
    \forall e \forall i: x_{ei} \in \{0, 1\}, y_{e} \in \{0, 1\} \\
    $$
    where
    \begin{align*}        x_{ei} = \begin{cases}
                1, \  \text{if edge $e$ has color $i$} \\
                0, \  \text{otherwise}
        \end{cases} & \text{and} &
            y_{e} = \begin{cases}
                1, \  \text{if edge $e$ is rich} \\
                0, \  \text{otherwise.}
            \end{cases}
    \end{align*}
     We will determine at what point the computation of rich-neighbor edge coloring becomes too intense for this technique and we will then use the random search algorythm.

     \subsection{Random Search}
        By creating a random search algorythm that will check if the conjecture holds for a class of graphs that are too large to be checked individually. Our plan is to create a random graph generator that will generate a regular graph with a given number of verticies and edges. Then we will check if the conjecture holds for the generated graph and we will repeat this process for a given number of times. Then we will repeat this process for different classes of graphs. The algorythm will be implemented in SageMath and its pseudocode is as follows:


\end{document}